### 2021-09-09 paper/localpsf.tex
figured out more direct proof of weighting function thing

In Algorithm \ref{alg:weighting_functions_incremental}, we show how to efficiently compute the functions $w_i$. Briefly:
\begin{enumerate}
\item For each sample point $x_i$, we compute a function $\psi_i$ by solving the following Neumann Poisson problem:
\begin{equation}
\label{eq:psi_eq}
\begin{cases}
\Delta \psi_i = \delta_{x_i} - 1/|\Omega|, & \text{in }\Omega, \\
\nu \cdot \nabla \psi_i = 0 & \text{on } \partial \Omega,
\end{cases}
\end{equation}
with condition $\int_\Omega \psi_i(x) dx = 0$. Here $\delta_{x_i}$ is the point source centered at $x_i$, $|\Omega|$ is the measure of the domain $\Omega$, and $\nu$ is the normal vector to $\partial \Omega$.
\item For each function $\psi_i$, we compute a function $\theta_i$ by solving another Neumann Poisson problem:
\begin{equation}
\label{eq:theta_eq}
\begin{cases}
\Delta \theta_i = \psi_i, & \text{in }\Omega, \\
\nu \cdot \nabla \theta_i = 0 & \text{on } \partial \Omega,
\end{cases}
\end{equation}
with condition $\int_\Omega \theta_i(x) dx = 0$.
%\item For each sample point $x_i$, we solve the Poisson equation with pure Neumann boundary conditions, using $\delta_{x_i}$ (a point source centered at $x_i$) as the right hand side source. We call the solution to this first Poisson problem $\psi_i$.
%\item For each function $\psi_i$, we solve the Poisson equation with pure Neumann boundary conditions, using $\psi_i$ as the right hand side source. We call the solution to this second Poisson problem $\theta_i$.
\item We form $w_i$ as a linear combination of the functions $\theta_i$, and the constant function $C(x)=1$. Details for this linear combination are given in Algorithm \ref{alg:weighting_functions_incremental}. 
\end{enumerate}
In Theorem \ref{thm:wi_alg_is_correct}, we prove that the functions $w_i$ produced by this process indeed solve optimization problem \eqref{eq:wi_optimization_problem}.

Constructing all $r$ of the functions $w_i$ requires solving the Poisson equation $2r$ times with different right hand side sources, and these Poisson PDE solves can be performed cheaply with multigrid. All of the weighting functions, $\{w_i\}_{i=1}^r$, will change if a new point, $x_{r+1}$, is added. However, the dominant computational cost in constructing the weighting functions is the solution of the Poisson PDEs, and these Poisson PDE solves can be performed incrementally---by storing the functions $\psi_i$ and $\theta_i$, we only need to perform two new Poisson PDE solves when a new point is added.
%, rather than $2(r+1)$ new PDE solves.

>>>>

For each $i=1,\dots,r$, optimization problem \eqref{eq:wi_optimization_problem} is an example of the following generic omtimization problem:
\begin{equation}
\label{eq:wi_optimization_problem_generic}
\begin{aligned}
\min_{v \in H^2_N(\Omega)} &\quad \frac{1}{2}\norm{\Delta v}_{L^2(\Omega)}^2 \\
\text{such that} &\quad v(x_j) = v_j, \quad j=1,\dots,r,
\end{aligned}
\end{equation}
where $v_j \in \mathbb{R}$, $j=1,\dots,r$ are now arbitrary function values that $v$ must take at the points $x_j$. We solve \eqref{eq:wi_optimization_problem_generic} efficiently via the following procedure:
\begin{enumerate}
\item For each sample point $x_i$, we compute a function $\psi_i$ by solving the following Neumann Poisson problem:
\begin{equation}
\label{eq:psi_eq}
\begin{cases}
\Delta \psi_i = \delta_{x_i} - 1/|\Omega|, & \text{in }\Omega, \\
\nu \cdot \nabla \psi_i = 0 & \text{on } \partial \Omega,
\end{cases}
\end{equation}
with condition $\int_\Omega \psi_i(x) dx = 0$. Here $\delta_{x_i}$ is the point source centered at $x_i$, $|\Omega|$ is the measure of the domain $\Omega$, and $\nu$ is the normal vector to $\partial \Omega$.
\item For each function $\psi_i$, we compute a function $\theta_i$ by solving another Neumann Poisson problem:
\begin{equation}
\label{eq:theta_eq}
\begin{cases}
\Delta \theta_i = \psi_i, & \text{in }\Omega, \\
\nu \cdot \nabla \theta_i = 0 & \text{on } \partial \Omega,
\end{cases}
\end{equation}
with condition $\int_\Omega \theta_i(x) dx = 0$.
%\item For each sample point $x_i$, we solve the Poisson equation with pure Neumann boundary conditions, using $\delta_{x_i}$ (a point source centered at $x_i$) as the right hand side source. We call the solution to this first Poisson problem $\psi_i$.
%\item For each function $\psi_i$, we solve the Poisson equation with pure Neumann boundary conditions, using $\psi_i$ as the right hand side source. We call the solution to this second Poisson problem $\theta_i$.
\item We form $f$ as follows:
\begin{equation*}
v(x) := \beta + \sum_{i=1}^r c_i \theta_i(x),
\end{equation*}
where the constants $c_i \in \mathbb{R}$, $i=1,\dots,r$, and $\beta \in \mathbb{R}$ are computed by solving the following linear system:
\begin{equation}
	\label{eq:interpolation_linear_system}
	\begin{bmatrix}
	S & \mathbf{1} \\ \mathbf{1}^T & 0
	\end{bmatrix}
	\begin{bmatrix}
	\mathbf{c} \\ \beta
	\end{bmatrix}
	=
	\begin{bmatrix}
	\mathbf{v} \\ 0
	\end{bmatrix}.
\end{equation}
Here $\mathbf{c} \in \mathbb{R}^r$ is the vector with $i$th component $c_i$, $\mathbf{1} \in \mathbf{R}^r$ is the column vector of all ones, $\mathbf{v} \in \mathbb{R}^r$ is the vector with $i$th component $v_i$, and $S \in \mathbb{R}^{r \times r}$ is the matrix with entries given by
\begin{equation*}
S_{ij} := \int_\Omega \psi_i(x) \psi_j(x) dx.
\end{equation*}
\end{enumerate}
In Theorem \ref{thm:wi_alg_is_correct}, we prove that the function $v$ produced by this process indeed solves optimization problem \eqref{eq:wi_optimization_problem_generic}.

Constructing all $r$ of the functions $w_i$ thus requires solving the Poisson equation $2r$ times with different right hand side sources to form the functions $\psi_i$ and $\theta_i$, and these Poisson PDE solves can be performed cheaply with multigrid. All of the weighting functions, $\{w_i\}_{i=1}^r$, will change if a new point, $x_{r+1}$, is added. However, the dominant computational cost in constructing the weighting functions is the solution of the Poisson PDEs, and these Poisson PDE solves can be performed incrementally---we only need to compute functions $\psi_i$ and $\theta_i$ associated with the new points. 
%, rather than $2(r+1)$ new PDE solves.
